---
title: "Homework 1 GitHub and R Practice"
author: "Melanie Beebe"
format: html
editor: visual
---

## Data Science Questions

### My view of what data science is

Data science is using very large sets of data to gain meaningful insights to answer relevant questions for a business. It uses a large array of applications to do so and as such is multidisciplinary and often requires a team of members with expertise in different areas.

### Differences and Similarities between data scientists and statisticians

-   both work with data

    -   statisticians work with smaller, often structured data sets

    -   data scientists work with data sets that are often too large to have on one computer and is often structured and unstructured, which requires a lot of preprocessing and wrangling

-   both analyze data

    -   statisticians focus on modeling data and making inference, bring data to models

    -   data scientists are more involved in data collection and the systems that analyze the data to answer questions of interest, bring models to data

### How I view myself in relation to these areas

I am in the Masters of Statistics program and don't expect to have a close relationship with data science. I had actually considered data science at one point but at the time it didn't seem very well defined and as a scientist felt that statistics would allow me to have a closer relationship to science. In some ways I guess you could consider a statistician a simpler form of a data scientist.

## R code using iris data

```{r}
#define object
y <- density(iris$Sepal.Length)
#identify class
class(y)
#identify type
typeof(y)
#view structure
str(y)
```

```{r}
#| echo: false
#plot y, iris sepal length density
plot(y)
```

